An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data

### 2018-10-16 paper/main.tex
added timecorr version of ISFC

We can generalize this formula to compute time-varying correlations by
incorporating a \textit{weight function} that takes a time $t$ as input,
and returns how much the observed data every timepoint (including $t$)
contribute to the correlations at time $t$ (Fig.~\ref{fig:weights}).
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/kernels}
  \caption{\textbf{Examples of time-varying weights.  Each panel
      displays per-timepoint weights at $t = 50$, evaluated for 100
      timepoints ($1, ..., 100$).  a. Uniform weights.} The weights
    are timepoint-invariant; observations at all timepoints are
    weighted equally, and do not change as a function of $t$.  This is
    a special case of weight function that reduces dynamic
    correlations to static correlations.  \textbf{b. Dirac delta
      function.} Only the observation at timepoint $t$ is given weight
    (of 1), and weights for observations at all other timepoints are
    set to 0.  \textbf{c. Gaussian weights.} Each observation's
    weights fall off in time according to a Gaussian probability
    density function centered on $\mu = t$.  Weights derived using
    several different example variance parameters ($\sigma^2$ are
    displayed.  \textbf{d. Laplace weights.}  Each observation's
    weights fall off in time according to a Laplace probability
    density function centered on $\mu = t$.  Weights derived using
    several different example scale parameters ($b$) are displayed.
    \textbf{e. Mexican hat (Ricker wavelet) weights.}  Each
    observation's weights fall off in time according to a Ricker
    wavelet centered on $t$.  Weights derived using several different
    example width parameters ($\sigma$) are displayed.}
  \label{fig:weights}
\end{figure}

@@

@@

\subsection*{Timepoint decoding}
Cite HTFA paper, summarize relevant methods.

>>>>

We can generalize this formula to compute time-varying correlations by
incorporating a \textit{weight function} that takes a time $t$ as input,
and returns how much the observed data every timepoint (including $t$)
contribute to the correlations at time $t$ (Fig.~\ref{fig:weights}).
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/kernels}
  \caption{\textbf{Examples of time-varying weights.  Each panel
      displays per-timepoint weights at $t = 50$, evaluated for 100
      timepoints ($1, ..., 100$).  a. Uniform weights.} The weights
    are timepoint-invariant; observations at all timepoints are
    weighted equally, and do not change as a function of $t$.  This is
    a special case of weight function that reduces dynamic
    correlations to static correlations.  \textbf{b. Dirac delta
      function.} Only the observation at timepoint $t$ is given weight
    (of 1), and weights for observations at all other timepoints are
    set to 0.  \textbf{c. Gaussian weights.} Each observation's
    weights fall off in time according to a Gaussian probability
    density function centered on $\mu = t$.  Weights derived using
    several different example variance parameters ($\sigma^2$ are
    displayed.  \textbf{d. Laplace weights.}  Each observation's
    weights fall off in time according to a Laplace probability
    density function centered on $\mu = t$.  Weights derived using
    several different example scale parameters ($b$) are displayed.
    \textbf{e. Mexican hat (Ricker wavelet) weights.}  Each
    observation's weights fall off in time according to a Ricker
    wavelet centered on $t$.  This function highlights the
    \textit{contrasts} between local versus surrounding activity
    patterns in estimating dynamic correlations. Weights derived using
    several different example width parameters ($\sigma$) are
    displayed.  }
  \label{fig:weights}
\end{figure}

@@

\subsubsection*{Inter-subject dynamic correlations}
Equation~\ref{eqn:timecorr} provides a means of taking a single
observation matrix, $\mathbf{X}$ and estimating the dynamic
correlations from moment to moment, $\mathbf{Y}$.  Suppose that one
has access to a set of multiple observation matrices that reflect the
same phenomenon.  For example, one might collect neuroimaging data
from several experimental participants, as each participant performs
the same task (or sequence of tasks).  Let $\{ mathbf{X}_1,
mathbf{X}_2, ..., mathbf{X}_P\}$ reflect the $T$ by $F$ observation
matrices for each of $P$ participants in an experiment.  We can use
\textit{inter-subject functional connectivity}~\citep[ISFC;
][]{SimoEtal16} to compute the degree of stimulus-driven correlations
reflected in the multi-participant dataset at a given timepoint $t$
using:
\begin{align}
\bar{\mathbf{C}}(t) = M\left(R\left(\frac{1}{2P} \sum_{i=1}^P
  Z\left(Y_i(t)\right)^\mathrm{T} + Z\left(Y_i,(t)\right)\right)\right),
\end{align}
where $M$ extracts and vectorizes the diagonal and upper triangle of a symmetric
matrix, $Z$ is the Fisher $z$-transformation~\citep{Zar10}:
\begin{align}
Z(r) = \frac{\log(1+r) - \log(1-r)}{2}
\end{align}
$R$ is the inverse of $Z$:
\begin{align}
R(z) = \frac{\exp(2z - 1)}{\exp(2z + 1)},
\end{align}
and $\mathbf{Y}_i(t)$ denotes the correlation matrix
(Eqn.~\ref{eqn:corr}) between each column of $\mathbf{X}_i$ and each
column of the average observations from all \textit{other}
participants, $\bar{\mathbf{X}}_{ \backslash i}$:
\begin{align}
  \bar{\mathbf{X}}_{ \backslash i} = R\left(\frac{1}{P-1}\sum_{i \in \backslash i} Z(\mathbf{X}_i\right),
\end{align}
where $ \backslash i$ denotes the set of all participants other than
participant $i$. In this way, the $T$ by $\left( \frac{F^2 - F}{2}
  + F \right)$
matrix $\bar{\mathbf{C}}$ is the time-varying extension of the ISFC
approach developed by \cite{SimoEtal16}.

@@

\subsection*{Timepoint decoding}

Cite HTFA paper, summarize relevant methods.
